Bip32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys

### 2024-05-23 paper.tex
clean up intro description of Secp and Ed25519

Bitcoin relies on the Secp256k1~\cite{Secp256k1} elliptic curve, which has a linear key space. A new public key can be formed by adding $[x]B$ to the public key $[k]B$, where $x$ and $k$ are private keys/scalars and $B$ the base point. This results in a new public key whose private key is $[x] + [k] \text{ mod } q$ for $q$ the order of the field.

An alternate elliptic curve standard for digital signatures is Ed25519~\cite{Ed25519}. It is used by a number of blockchains such as Algorand~\cite{AlgorandEd25519}, Cardano~\cite{CardanoEd25519}, Monero~\cite{MoneroEd25519}, Nano~\cite{NanoEd25519}, Solana~\cite{SolanaEd25519} and more. Polkadot~\cite{PolkadotEd25519} uses a variant called Schnorrkel/Ristretto x25519 (``sr25519'') and Tezos~\cite{TezosEd25519} offers it alongside other curves.

Ed25519 has a number of advantages, such as high speed constant-time implementations and a signing procedure where the nonce is deterministically derived from the data to be signed (mitigating the kind of attack that Sony PS3 suffered~\cite{Ed25519}).

>>>>

Bitcoin relies on the Secp256k1~\cite{Secp256k1} elliptic curve, which has a linear key space.
A new public key can be formed by adding $[x]B$ to the public key $[k]B$, where $x$ and $k$ are private keys (scalars), and $B$ is the base point.
This results in a new public key whose private key is $[x] + [k] \bmod q$, where $q$ is the order of the field.

An alternative elliptic-curve standard for digital signatures is Ed25519~\cite{Ed25519}.
It is used by a number of blockchains such as Algorand~\cite{AlgorandEd25519}, Cardano~\cite{CardanoEd25519}, Monero~\cite{MoneroEd25519}, Nano~\cite{NanoEd25519}, Solana~\cite{SolanaEd25519}, and more.
Polkadot~\cite{PolkadotEd25519} uses a variant called Schnorrkel/Ristretto x25519 (``sr25519'') and Tezos~\cite{TezosEd25519} offers it alongside other curves.

Ed25519 has a number of advantages, such as high-speed constant-time implementations, and a signing procedure where the nonce is deterministically derived from the data to be signed (mitigating the kind of attack that Sony PS3 suffered).
